---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Analytical-approaches-for-acoustic-data-2023

<!-- badges: start -->
<!-- badges: end -->

## This is the GitHub repository for the Analytical Approaches for Acoustic Data Lab for the NTRES 3150 Intro Conservation Bioacoustics Fall 2023 course. 

### This repository contains three R scripts:  

Part 1. Exploratory analysis of different sound classes.R

Part 2. Biodiversity in different landuse types in Borneo.R

Part 3. Design your own study in sapsucker woods.R

### And one RMarkdown template to answer questions related to the lab exercises:  

Analytical approaches for acoustic data lab questions.Rmd. 

### Here is a link to the sound file we will use for Part 1. 
https://drive.google.com/file/d/1mV-uvbqbCtZ1DV0yXARuX7g60GBiSqAO/view?usp=sharing

```{r, echo=FALSE, fig.cap="Figure 1. Spectrogram of a gibbon female call from Part 1 of the lab exercises"}
# Now we can make a spectrogram. First lets read in the .wav file
FemaleGibbonFile <- tuneR::readWave("data/ExploratoryAnalysis/SoundFiles/female.gibbon_2.wav")

# There are many different packages that you can use to create spectrograms; here are two
seewave::spectro(FemaleGibbonFile,flim=c(0,2.5))
```

